---
title: "Technická dokumentace"
output:
  html_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(details)
```

```{r, child="README.md"}
```

## How to reproduce

- load data and metadata by running numbered R scripts in order. This relies on input XLSX files being in `data-input`
- run `rmarkdown::render_site()` or run numbered RMarkdown scripts in order

or run `build-and-render.R`.

To subsequently build the site afresh and deploy to Netlify, run `build-site-and-deploy.sh`.

Environment reproducibility is maintained using `renv`. This means that upon running R in the project folder, all the necessary packages will be installed in a local library (in fact, installed in a cache from which they can be reused, and linked into the local project library where they take up no space.) Should this fail, you can run `renv::deactivate()` and install the packages manually, though you might end up with different versions.

## Reproducibility log

```{details, details.summary = "Time", echo = FALSE}
Sys.time()
```
```{details, details.summary = "Session Info", echo = FALSE}
sessioninfo::session_info()
```

```{details, details.summary = "Version control", echo = FALSE}
git2r::repository()
```

```{details, details.summary = "renv status", echo = FALSE}
print(renv::status())
```

