---
title: "Technická dokumentace"
output:
  html_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(details)
```

```{r, child="README.md"}
```

## How to reproduce

First, install all the necessary R packages: run `renv::restore()` (this only needs to be done once and only rerun if the `renv.lock` file changes.)

Then:

- load and transform data and metadata by running numbered R scripts in order. This relies on input XLSX files being in `data-input`, in a subdirectory set in the `pth` variable in `01_load-data.Rmd`
- run `rmarkdown::render_site()` or run numbered RMarkdown scripts in order

or run `build-and-render.R` to run both these steps.

To subsequently build the site afresh and deploy to Netlify

- on a Linux/Mac machine, run `build-site-and-deploy.sh`; this requires the [Netlify CLI](https://docs.netlify.com/cli/get-started/)
- or deploy the `docs` folder to Netlify [using other means](https://docs.netlify.com/site-deploys/create-deploys/).

Environment reproducibility is maintained using `renv`. This means that upon running R in the project folder, all the necessary packages will be installed in a local library by running `renv::restore()` (in fact, installed in a cache from which they can be reused, and linked into the local project library where they take up no space.) Should this fail, you can run `renv::deactivate()` and install the packages manually, though you might end up with different versions.

## Reproducibility log

```{details, details.summary = "Time", echo = FALSE}
Sys.time()
```
```{details, details.summary = "Session Info", echo = FALSE}
sessioninfo::session_info()
```

```{details, details.summary = "Version control", echo = FALSE}
git2r::repository()
```

```{details, details.summary = "renv status", echo = FALSE}
print(renv::status())
```

